Binary companions of red giant stars with APOGEE: \\ catalog and companions that survive the common envelope

### 2018-01-21 paper/1-catalog/twoface-catalog.tex
helpers
minor changes

\begin{abstract}\noindent % trust me
% Context
Repeat radial-velocity measurements of stars can be used to identify stellar-,
sub-stellar, and planetary-mass companions.
Even few observations are useful for detecting companions, though such data are
difficult to use for constraining the physical properties of companions because
permitted orbital solutions are highly degenerate.
% Aims
Here we perform a search for secondary companions of red giant branch (\RGB)
stars using data from the \apogee\ survey (\DR), which has measured multi-epoch
($\geq 3$) but sparse radial velocities for $> 80,000$ \RGB\ stars.
In some cases, where the primary-star masses are known, the mass-function
degeneracy is broken and the secondary-companion masses ($m_2\,\sin i$) can be
inferred.
% Methods
We use a custom-built Monte Carlo sampler (\thejoker) combined with stellar
parameters and primary mass estimates to deliver (often highly multi-modal)
posterior beliefs about companion mass, pericenter distance, and other orbital
parameters for the stars.
We compare the companion populations of red clump (\RC) versus \RGB\ stars at
similar surface gravity and temperature, and study the metallicity dependence
of companion properties.
% Results
We provide a catalog of \ncompanions\ companions for which the companion
properties can be confidently determined, along with posterior samplings for all
\ntotal\ stars in the parent sample.
\todo{We find differences between the companions around \RC\ and \RGB\
stars that are in/consistent with the theoretical prediction that
stellar companions should not survive the common-envelope \RGB\ phase.}
\todo{We additionally find trends in XX with chemical abundances.}

@@

For each $n$ of $N$ RGB stars in APOGEE, we obtain $K$ posterior samples over
primary orbital parameters $\bs{w} = (P, e, \omega, \phi_0, K, v_0)$ and the
jitter parameter, $y = \ln s^2$, using {\it The Joker}.
To obtain this sampling, we use an interim prior on the jitter parameter
parametrized by a mean and root-variance $\alpha_0 = (\mu_{y,0}, \sigma_{y,0})$.

@@

It is a pleasure to thank XX.

>>>>

\begin{abstract}\noindent % trust me
% Context
Repeat radial-velocity measurements of stars can be used to identify stellar-,
sub-stellar, and planetary-mass companions.
Even few observations are useful for detecting companions, though such data are
difficult to use for constraining physical properties because permitted orbital
solutions are highly degenerate.
% Aims
Here we perform a search for secondary companions of stars observed by the
\apogee\ survey (\DR), which has measured multi-epoch ($\geq 3$) but sparse
radial velocities for close to 100,000 stars.
% Methods
We use a custom-built Monte Carlo sampler (\thejoker) to deliver (often highly
multi-modal) posterior beliefs about companion orbital parameters.
In some cases, where the primary-star masses are known, the mass-function
degeneracy is broken and the secondary-companion masses ($m_2\,\sin i$) can be
inferred.
% Results
We provide a catalog of \ncompanions\ companions for which the companion
properties can be confidently determined, along with posterior samplings for all
\ntotal\ stars in the parent sample.
\todo{We find differences between the companions around \RC\ and \RGB\
stars that are in/consistent with the theoretical prediction that
stellar companions should not survive the common-envelope \RGB\ phase.}
\todo{We additionally find trends in XX with chemical abundances.}

We compare the companion populations of red clump (\RC) versus \RGB\ stars at
similar surface gravity and temperature, and study the metallicity dependence
of companion properties.

@@

For each $n$ of $N$ RGB stars in APOGEE, we obtain $K$ posterior samples over
primary orbital parameters $\bs{w} = (P, e, \omega, \phi_0, K, v_0)$ and the
jitter parameter, $y = \ln s^2$, using \textit{The Joker}.
To obtain this sampling, we use an interim prior on the jitter parameter
parametrized by a mean and root-variance $\alpha_0 = (\mu_{y,0}, \sigma_{y,0})$.

@@

It is a pleasure to thank Keith Hawkins (Columbia), XXXXXXX.
